\textbf{NBA Party}

### 2017-07-04 init_model.rnw
Added markers to show why drinks and population won't work.

require(data.table)
require(ggplot2)
require(magrittr)
require(sampling)
require(stargazer)
set.seed(4052017)

@@

pdf('writing/why_drinks_or_population_dont_work.pdf', width = 16, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$log.nmusicians,
     main = 'Why drinking establishments or population don\'t work as a proxy for nightlife',
     ylab = 'Log sum of Variable',
     xlab = '', axes = F, pch = 1, ylim = c(0, max(tmp$log.population)), type = 'l')
points(x = ticks, y = tmp$log.ndrinks, pch = 16, col = 'purple', type = 'l')
points(x = ticks, y = tmp$log.population, pch = 18, col = 'orange', type = 'l')
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
legend(x = 1.5, y = 12.5, legend = c('Musicians and sound recording studios',
                                 'Drinking establishments and liquor stores',
                                 'Population'), pch = c(1, 16, 18), col = c('black', 'purple', 'orange'))
text(x = 3.6, y = 9.5, labels = paste("Correlation (alcohol):       ", 
                                       cor(tmp$log.nmusicians, tmp$log.ndrinks) %>% round(., 3)))
text(x = 3.6, y = 10, labels = paste("Correlation (population): ", 
                                       cor(tmp$log.nmusicians, tmp$log.population) %>% round(., 3)))
dev.off()

>>>>

require(hangover)
require(data.table)
require(ggplot2)
require(magrittr)
require(sampling)
require(stargazer)
set.seed(4052017)

@@

pdf('writing/why_drinks_or_population_dont_work.pdf', width = 16, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$log.nmusicians,
     main = 'Why drinking establishments or population don\'t work as a proxy for nightlife',
     ylab = 'Log sum of Variable',
     xlab = '', axes = F, pch = 1, ylim = c(0, max(tmp$log.population)), type = 'l')
points(x = ticks, y = tmp$log.ndrinks, pch = 16, col = 'purple', type = 'l')
points(x = ticks, y = tmp$log.population, pch = 18, col = 'orange', type = 'l')
### Houston has large population, but isn't necessarily known for nightlife.
segments(x0 = which(tmp$team == 'houston rockets'), 
         x1 = which(tmp$team == 'houston rockets'),
         y0 = -1,
         y1 = tmp[team == 'houston rockets', log.population], col = 'gray70', lty = 'dashed')
segments(x0 = which(tmp$team == 'houston rockets'), 
         x1 = length(ticks),
         y0 = tmp[team == 'houston rockets', log.population],
         y1 = tmp[team == 'houston rockets', log.population], col = 'gray70', lty = 'dashed')
abline(h = tmp[team == 'houston rockets', log.ndrinks], col = 'gray70', lty = 'dashed')
### New orleans is infamous for party, but Population places it at the bottom of the index.
segments(x0 = which(tmp$team == 'new orleans hornets'),
         x1 = which(tmp$team == 'new orleans hornets'), 
         y0 = -1, 
         y1 = tmp[team == 'new orleans hornets', log.population],col = 'gray70', lty = 'dashed')
segments(x0 = 0, x1 = which(tmp$team == 'new orleans hornets'),
         y0 = tmp[team == 'new orleans hornets', log.population],
         y1 = tmp[team == 'new orleans hornets', log.population], col = 'gray70', lty = 'dashed')
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>%
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
legend(x = 1.5, y = 12.5, legend = c('Musicians and sound recording studios',
                                 'Drinking establishments and liquor stores',
                                 'Population'), pch = c(1, 16, 18), col = c('black', 'purple', 'orange'))
text(x = 3.6, y = 9.5, labels = paste("Correlation (alcohol):       ", 
                                       cor(tmp$log.nmusicians, tmp$log.ndrinks) %>% round(., 3)))
text(x = 3.6, y = 10, labels = paste("Correlation (population): ", 
                                       cor(tmp$log.nmusicians, tmp$log.population) %>% round(., 3)))
dev.off()
